Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-22 paper/main.tex
fix close-quotes character

The Davos package is named after Davos Seaworth, a smuggler referred
to as ``the Onion Knight" from the series \textit{A Song of Ice and Fire} by
George R. R. Martin~\cite{Mart98}. The \texttt{smuggle} keyword provided by
Davos is a play on Python's \texttt{import} keyword: whereas importing
can load a package into the Python workspace within the existing rules and
frameworks provided by the Python language, ``smuggling'' provides an
alternative that expands the scope and reach of ``importing.'' Like the
character Davos Seaworth (who became famous for smuggling onions through a
blockade on his homeland), we use ``onion'' comments to precisely control how
packages are smuggled into the Python workspace.

>>>>

The Davos package is named after Davos Seaworth, a smuggler referred
to as ``the Onion Knight'' from the series \textit{A Song of Ice and Fire} by
George R. R. Martin~\cite{Mart98}. The \texttt{smuggle} keyword provided by
Davos is a play on Python's \texttt{import} keyword: whereas importing
can load a package into the Python workspace within the existing rules and
frameworks provided by the Python language, ``smuggling'' provides an
alternative that expands the scope and reach of ``importing.'' Like the
character Davos Seaworth (who became famous for smuggling onions through a
blockade on his homeland), we use ``onion'' comments to precisely control how
packages are smuggled into the Python workspace.
